Fractional Types

### 2013-02-25 frac.tex

\noindent 
Types include the unit type {{1}}, sum types {{b1+b2}}, and
products types {{b1*b2}}.  Values includes {{()}} which is the only value of
type {{1}}, {{left v}} and {{right v}} which inject~{{v}} into a sum type,
and {{(v1,v2)}} which builds a value of product type. 
%% But these values should be regarded as largely ancillary: we do not
%% treat them as first-class citizens, and they only occur when observing
%% the effect of an isomorphism.

>>>>

\noindent 
Types include the unit type {{1}}, sum types {{b1+b2}}, and
product types {{b1*b2}}.  Values include {{()}} which is the only value of
type {{1}}, {{left v}} and {{right v}} which inject~{{v}} into a sum type,
and {{(v1,v2)}} which builds a value of product type. 
%% But these values should be regarded as largely ancillary: we do not
%% treat them as first-class citizens, and they only occur when observing
%% the effect of an isomorphism.
